---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE
)
```

```{r attach-libraries}
library(dplyr)
library(tidyr)
library(tibble)
library(rvest)
library(ggplot2)
library(polite)
library(stringr)
library(lubridate)
library(purrr)
library(knitr)
library(emo)
library(ggwordcloud)
```

```{r scrape-blog}
scrape_ryon7 <- function(base_url = "https://ryo-n7.github.io/") {
  
  session <- polite::bow(base_url)
  
  blog_titles <- scrape(session) %>% 
    html_nodes(".post-title") %>% 
    html_text()
  
  blog_links <- scrape(session) %>% 
    html_nodes(".post-read-more") %>% 
    html_attr("href")
  
  blog_dates <- scrape(session) %>% 
    html_nodes(".post-meta") %>% 
    html_text()
  
  blog_dates_clean <- blog_dates %>% 
    str_trim() %>% 
    str_remove_all("Posted on ")
  
  blog_tags <- scrape(session) %>% 
    html_nodes(".blog-tags") %>% 
    html_text()
  
  blog_tags_clean <- blog_tags %>% 
    str_trim() %>% 
    str_remove_all("Tags:\n") %>% 
    str_replace_all("[:space:]", "") %>% 
    str_remove_all(",r-bloggers")
  
  posts_data <- tibble(blog_dates_clean, blog_titles, blog_tags_clean) %>% 
    transmute(
      n = nrow(.):1,
      publish_date = mdy(blog_dates_clean),
      title = blog_titles,
      tags = blog_tags_clean,
      link = paste0(base_url, blog_links)
    )
  return(posts_data)
}

posts_df <- scrape_ryon7(base_url = "https://ryo-n7.github.io/")
```

```{r publish-plot}
publish_plot <- posts_df %>% 
  ggplot(aes(x = publish_date, y = 1)) + 
  geom_point(shape = "|", size = 10, stroke = 1, color = "#1D8016") + 
  theme_void()
```

```{r tags-wordcloud}
tags_count_df <- posts_df$tags %>% 
  paste0(collapse = ",") %>% 
  str_replace_all(",", ", ") %>% 
  as_tibble_col(column_name = "tag") %>% 
  separate_rows(tag, sep = ",") %>% 
  group_by(tag) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

# redcol <- c('#fb6a4a','#ef3b2c','#cb181d','#a50f15','#67000d') #%>% rev()
greencol <- c('#74c476','#41ab5d','#238b45','#006d2c','#00441b')
# colorVec = rep(c('red', 'skyblue'), length.out=nrow(demoFreq))

# wordcloud2(demoFreq, color = colorVec, fontWeight = "bold")
# wordcloud2::wordcloud2(tags_count_df, fontFamily = "Roboto Slab", color = redcol)

tags_wordcloud <- tags_count_df %>% 
  ggplot(aes(label = tag, size = n, color = n)) +
  geom_text_wordcloud(shape = "diamond") +
  scale_size_area(max_size = 12) +
  scale_color_gradientn(colours = greencol) +
  theme_minimal() 
```


# Ryo-N7.github.io

<!-- badges: start -->
[![ko-fi](https://ko-fi.com/img/githubbutton_sm.svg)](https://ko-fi.com/O4O342A2A)
<!-- badges: end -->

This is the Github repository for my website, [R_by_Ryo](https://ryo-n7.github.io/)! 

Usually about soccer, R conference/meetup roundups (RStudio, UseR!, TokyoR, etc.), and other data science-y things - all done in R.

# Expected Blog (xBlog) Stats

`r emo::ji("star")` There have been `r nrow(posts_df)` posts on the blog since `r min(posts_df$publish_date)`. 

`r emo::ji("date")` That's about a post every `r round((as.numeric(today() - min(posts_df$publish_date))) / nrow(posts_df))` days, or about `r round(((nrow(posts_df) / (as.numeric(today() - min(posts_df$publish_date)))) * 30), 1)` posts per month.

`r emo::ji("new")` The latest post was published `r today() - max(posts_df$publish_date)` day(s) ago: [`r posts_df$title[1]`](`r posts_df$link[1]`).

`r emo::ji("chart_with_upwards_trend")` This 2D plot shows posts over time:

```{r plot-out, fig.height=1, fig.width=10, fig.alt="A 2D chart where each point represents a post on an axis of time spanning from 2018 to the present. There are some gaps, but posts have been relatively consistent over time."}
publish_plot
```

Below is a word cloud of all the different tags on my blog posts, it seems I mostly blog about "`r tags_count_df %>% top_n(1) %>% pull(tag)`":

```{r plot-wordcloud, fig.height=5, fig.width=10}
tags_wordcloud
```

<details><summary> Click to expand a full list of my blog posts</summary>
```{r posts-table}
posts_df %>% 
  transmute(
    Number = n, 
    Date = publish_date, 
    Title = paste0("[", title, "](", link, ")")
  ) %>% 
  kable()
```
</details>


_Last Updated `r today()`_
